A pipeline to analyse time-course gene expression data

### 2020-06-05 scripts/manuscript.Rmd
changes to introduction/installation

- Make clear that it applies to RNASeq and how to call the different functions
    to RNASeq
- Check that clustering can deal with count data.

*EAP*: What is your plan for the installation instructions Nelle? Shouldn't it be moved where we introduce the package, and give instructions about how to install it there.

@@

@@

## Package versions

The following packages are needed for this workflow.

To install `moanin` directly from GitHub, use the devtools' `install_github`
function:

```{r eval=FALSE}
library(devtools)
install_github("NelleV/moanin")

library(moanin)
```

@@

```{r display_lfc}
kable(log_fold_change_timecourse[1:5, ], digits=3, booktabs=TRUE, escape=F)
```

>>>>

- Make clear that it applies to RNASeq and how to call the different functions
    to RNASeq
- Check that clustering can deal with count data.
- Update Nelle's affiliation!

@@

## Installation and setup

 `moanin` is available from GitHub, and can be installed using the `install_github` function in the package `devtools`:

```{r eval=FALSE}
library(devtools)
install_github("NelleV/moanin")
library(moanin)
```

The following additional packages are needed for this workflow:

**EAP**: Why is this list not the same as the (hidden via echo=FALSE) list at the beginning of the document? I also needed to install `BiocWorkflowTools`, `KEGGprofile` to run the .Rmd

@@

@@

```{r display_lfc}
kable(log_fold_change_timecourse[1:5, ], digits=3, booktabs=TRUE)
```
